### 2014-02-23 paper/retrofit.tex
inlinging thread pool

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie |  IT te
iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie |  IT tE
io   ::=  (il, id ie)
Q    ::=  nil | io , Q

@@

iTE  ::=  THole | iTE, lconf id il tS ie

@@

\begin{mathpar}
\inferrule[I-evalCtx]
{|
iconf iS (tconf id il ie)
.->
iconf iS' (tconf id il' ie')
|}
{|
iS ,(iniTE (lconf id il tS (iniE ie)))
.-.>
iS', (iniTE (lconf id il' tS (iniE ie')))
|}

\and
\inferrule[I-evalCtx2]
{|
iS ,(iniTE (lconf id il tS ie))
.-.>
iS', (iniTE' (lconf id il' tS ie'))
|}
{|
iS ,(iniTE (lconf id il tS (iniE ie)))
.-.>
iS', (iniTE' (lconf id il' tS (iniE ie')))
|}

\and
\inferrule[I-step]
{|
conf tS (te) -> conf tS' te'
|}
{|
iS, (iniTE (lconf id il tS (IT te)))
.-.>
iS, (iniTE (lconf id il tS' (IT te')))
|}

@@

\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = q(tS)|\\
|fresh (id')|\\
|iTE' THole = iniTE (lconf id il tS id'), THole|
}
{|
iS, iniTE (lconf id il tS (fork ie))
.-.>
iS', iniTE' (lconf id' il tS' (TI ie))
|}
%{|fresh (id')|}

@@

>>>>

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit | IT tv
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie |  IT te
iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie |  IT tE
io   ::=  (il, id ie)
Q    ::=  nil | io , Q

@@

@@

\begin{mathpar}
\inferrule[I-evalCtx]
{|
iconf iS (tconf id il ie)
.->
iconf iS' (tconf id il' ie')
|}
{|
iconf iS (lconf id il tS (iniE ie), ldots)
.->
iS' ; sched step (lconf id il' tS (iniE ie'), ldots)
|}

\and
\inferrule[I-done]
{|
|}
{|
iconf iS (lconf id il tS iv, ldots)
.->
iS ; sched done (lconf id il tS iv, ldots)
|}

\and
\inferrule[I-stepT]
{|
conf tS (te) -> conf tS' te'
|}
{|
iconf iS (lconf id il tS (iniE (IT te)), ldots)
.->
iS ; sched step (lconf id il tS' (iniE (IT te')), ldots)
|}

\and
\inferrule[I-noStepT]
{|
conf tS (te) -/> 
|}
{|
iconf iS (lconf id il tS (iniE (IT te)), ldots)
.->
iS ; sched noStep (lconf id il tS (iniE (IT te)), ldots)
|}

\and
\inferrule[I-noStep]
{|
it .-/> 
|}
{|
iconf iS (it, ldots)
.->
iS ; sched noStep (it, ldots)
|}

@@

\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = klone(tS)|\\
|it1 = lconf id il tS (iniE id')|\\
|itnew = lconf id' il tS' (TI ie)|\\
|fresh (id')|
}
{|
iconf iS (lconf id il tS (iniE (fork ie)), ldots)
.->
iS'; sched fork (it1, ldots, itnew)
|}
%{|fresh (id')|}

@@

\begin{figure}
  Round robin:
\begin{code}
  sched step (it1, it2, ...)    = {it2, ..., it1}
  sched done (it1, it2, ...)    = {it2, ...}
  sched noStep (it1, it2, ...)  = {it2, ...}
  sched fork (it1, it2, ...)    = {it2, ..., it1}
\end{code}
  Browbound:
\begin{code}
  sched step (it1, it2, ...)    = {it1, it2, ...}
  sched noStep (it1, it2, ...)  = {it2, ...}
  sched done (it1, it2, ...)    = {it2, ...}
  sched fork (it1, it2, ...)    = {it1, it2, ...}
\end{code}
  Sequential:
\begin{code}
  sched step (it1, it2, ...)       = {it1, it2, ...}
  sched noStep (it1, it2, ...)     = {it1, it2, ...}
  sched done (it1, it2, ...)       = {it2, ...}
  sched fork (it1, it2, ... it1n)  = {itn, it1, it2, ...}
\end{code}
\caption{scheduling policies}
\end{figure}
